maps

### 2022-11-09 code/maps.qmd
Change point size and color

```{r}
exome_points_map <- tm_shape(hillshade_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(nps_boundaries) + 
  tm_borders(col = "black") +
  tm_shape(exome_points) + 
  tm_symbols(size = 0.5, # increase point size, use darker blue
             col = "bd_status", 
             palette = c("#FFEC8B", "#87CEFA"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Bd status") +
  tm_layout(legend.position = c("right", "top")) +
  tm_compass(type = "4star",
             position = c("left", "bottom"),
             size = 2) +
  tm_scale_bar(breaks = c(0, 25, 50), 
               text.size = 0.7, 
               position = c("left", "bottom"))

>>>>

```{r}
exome_points_map <- tm_shape(hillshade_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(nps_boundaries) + 
  tm_borders(col = "black") +
  tm_shape(exome_points) + 
  tm_symbols(size = 0.7, # increase point size, use darker blue
             col = "bd_status", 
             palette = c("#FFEC8B", "#00B2EE"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Bd status") +
  tm_layout(legend.position = c("right", "top")) +
  tm_compass(type = "4star",
             position = c("left", "bottom"),
             size = 2) +
  tm_scale_bar(breaks = c(0, 25, 50), 
               text.size = 0.7, 
               position = c("left", "bottom"))
